\systemEnding: Bootstrapping Domain-Specific Languages for Neurally-Guided Bayesian Program Learning

### 2019-01-01 archive.tex
new learning curves

\begin{figure}
  \includegraphics[width = \textwidth]{figures/DeepLogo.pdf} 
  \end{figure}

@@

\begin{figure}
  \begin{tabular}{ccc}
    \includegraphics[width = 5cm]{figures/logoLearningCurve.png}&
    \includegraphics[width = 5cm]{figures/textLearningCurve_batch.png}&
    \includegraphics[width = 5cm]{figures/listLearningCurve_batch.png}\\
    \includegraphics[width = 5cm]{figures/towerLearningCurve_batch.png}&
    \includegraphics[width = 5cm]{figures/rationalLearningCurve_batched.png}&
  \end{tabular}
  \caption{}\label{learningCurves}
\end{figure}

>>>>

\begin{figure}
  \includegraphics[width = \textwidth]{figures/DeepLogo.pdf}
  \caption{\textbf{Bottom}: Learned graphics programing DSL. Each circle encloses a different learned component; arrows point from a component to other components that use it. \textbf{Top}: 3 tasks, and below them the programs that solve them. Yellow/Blue/Green highlighting indicates which DSL components are used to solve which tasks.}
  \end{figure}

@@

\begin{figure}
  \begin{tabular}{ccc}
    \includegraphics[width = 5cm]{figures/logoLearningCurve_batch.png}&
    \includegraphics[width = 5cm]{figures/textLearningCurve_batch.png}&
    \includegraphics[width = 5cm]{figures/listLearningCurve_batch.png}\\\\
    \includegraphics[width = 5cm]{figures/towerLearningCurve_batch.png}&
    \includegraphics[width = 5cm]{figures/rationalLearningCurve_batch.png}&
  \end{tabular}
  \caption{}\label{learningCurves}
\end{figure}
